Query Optimization for Dynamic Imputation

### 2017-03-02 paper/conclusion.tex
paper: add itemize to conclusion

\textbf{Imputation confidence:} Obtaining confidence measures for query results
produced when missing values are imputed with a statistical model is
another possible improvement to the system. These measures could be obtained in general
using resampling methods like cross-validation and bootstrapping\cite{kohavi1995study}.
In contrast to standard confidence calculations, one added complexity is that
imputation takes place at various points in the plan, so the composition of results
through standard query operations needs to be taken into account when computing confidence
measures.
In addition, multiple imputation could be used within query execution and confidence measures like variances could
similarly propagate through the query plan.

\textbf{Imputation operators:} We explored a subset of possible imputation operators.
In particular, we explored two variants of the \textit{Drop} and \textit{Impute} operations. The system
could be extended to consider a broader family of operators. As the search space grows,
there will likely be additional steps needed in order to avoid sub-optimal plans.

\textbf{Adaptive query planning:} Currently, the imputation is local to a given query, meaning
no information is shared across queries. An intriguing direction would be to take advantage
of imputation and execution data generated by repeated queries. Note that this goes beyond
simply caching imputation results, and instead could entail operations such as extending
intermediate results with prior imputation values to improve accuracy, or pruning out
query plans which have been shown to produce low-confidence imputations.

>>>>

\begin{itemize}
\item \textbf{Imputation confidence:} Obtaining confidence measures for query results
produced when missing values are imputed with a statistical model is
another possible improvement to the system. These measures could be obtained in general
using resampling methods like cross-validation and bootstrapping\cite{kohavi1995study}.
In contrast to standard confidence calculations, one added complexity is that
imputation takes place at various points in the plan, so the composition of results
through standard query operations needs to be taken into account when computing confidence
measures.
In addition, multiple imputation could be used within query execution and confidence measures like variances could
similarly propagate through the query plan.

\item \textbf{Imputation operators:} We explored a subset of possible imputation operators.
In particular, we explored two variants of the \textit{Drop} and \textit{Impute} operations. The system
could be extended to consider a broader family of operators. As the search space grows,
there will likely be additional steps needed in order to avoid sub-optimal plans.

\item \textbf{Adaptive query planning:} Currently, the imputation is local to a given query, meaning
no information is shared across queries. An intriguing direction would be to take advantage
of imputation and execution data generated by repeated queries. Note that this goes beyond
simply caching imputation results, and instead could entail operations such as extending
intermediate results with prior imputation values to improve accuracy, or pruning out
query plans which have been shown to produce low-confidence imputations.
\end{itemize}
